---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
<<<<<<< HEAD
```{r echo = FALSE}
library(ggplot2)
library(dplyr)
opts_chunk$set(echo = TRUE)
```

## Loading and preprocessing the data
```{r}
data = read.csv(file="activity.csv", header=TRUE,)
```

## What is mean total number of steps taken per day?
```{r}
by_day <- group_by(data, date)
by_day_summary <- summarize(group_by(data, date), total = sum(steps,na.rm=TRUE))
by_day_summary

qplot(by_day_summary$total, binwidth=3000)
```

Steps per day: Mean
```{r}
mean(by_day_summary$total)
```

Steps per day: Median
```{r}
median(by_day_summary$total)
```


## What is the average daily activity pattern?
```{r}
by_interval <- aggregate(steps ~ interval, data, mean)
qplot(y=by_interval$steps, x=by_interval$interval, geom="line")
```

5 minute interval with most steps averaged across all days is
```{r}
by_interval[which.max(x=by_interval$steps),1]
```
=======


## Loading and preprocessing the data



## What is mean total number of steps taken per day?



## What is the average daily activity pattern?

>>>>>>> 80edf39c3bb508fee88e3394542f967dd3fd3270


## Imputing missing values

<<<<<<< HEAD
Number of rows with missing values
```{r}
dim(data[data$steps == "NA",])[1]
```

Alternate dataset
```{r}
alternate_data <- data
for (i in 1:nrow(alternate_data)) {
  if (is.na(alternate_data[i,"steps"])) {
    alternate_data[i,"steps"] <- mean(data[data$date==alternate_data[i,"date"],"steps"])
  }
}

qplot(by_day_summary$total, binwidth=3000)
```

## Are there differences in activity patterns between weekdays and weekends?
```{r}
alternate_data <- mutate(alternate_data, day = weekdays(as.Date(data$date,format="%Y-%m-%d")))
alternate_data[alternate_data$day == "Saturday" | alternate_data$day == "Sunday", "day"] <- "weekend" 
alternate_data[alternate_data$day != "weekend", "day"] <- "weekday" 
alternate_data$day <- as.factor(alternate_data$day)

by_interval_alternate <- aggregate(steps ~ interval + day, alternate_data, mean)
qplot(y=steps, x=interval, data= by_interval_alternate, geom="line", facets=day ~ .)
```
=======


## Are there differences in activity patterns between weekdays and weekends?
>>>>>>> 80edf39c3bb508fee88e3394542f967dd3fd3270
